---
title: "Experiment 010"
subtitle: "Effect of Rapamycin on *wDah* and *DGRP OX* Survival to Systemic Infection with *P. rettgeri*"
author: "by Barbara Black"
date: "Last compiled on `r format(Sys.time(), '%d %B, %Y')`"
output: 
    html_document:
      code_folding: hide
      number_sections: true
      toc: true
      toc_float: true
      toc_depth: 3
      fig_caption: true
      theme: united
      css: style.css
      highlight: zenburn
editor_options: 
  chunk_output_type: console
---

<style>
/* Change font size of the title */
h1.title {
  font-size: 22px;
}

/* Define the frames */
div.blue { background-color:#e6f0ff; border-radius: 1px; padding: 10px; }
div.orange { background-color:#fff8dc; border-radius: 5px; padding: 20px; margin: 10px 0;}
div.green { background-color:#00bbc6; border-radius: 5px; padding: 20px;
  border: 1px solid #000; margin: 10px 0;}

/* Headers */ 
h1 { font-size: 18px; font-weight: bold;}
h2 { font-size: 16px; font-weight: bold; margin: 10px 0;}
h3 { font-size: 14px; font-weight: bold; margin: 10px 0;}

/* Change font size of the table of contents */
TOC { font-size: 12px; }
</style>

```{r chunk-setup}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, results = 'hide', dpi = 300)
```

```{r git-setup}
# Initialise a local Git repo
#usethis::use_git()

# Connect local Git repo to GitHub
#usethis::use_github()
```

# Background

# Code {.tabset}

## Functions

```{r survival-functions}
# function to change code chunk size in output
# note: automatically applied when chunk runs
def.chunk.hook = knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x = def.chunk.hook(x, options)
  ifelse(options$size != "normalsize", paste0("\n \\", options$size,"\n\n", x, "\n\n \\normalsize"), x)
})

# function to turn $censored into 'character' across all files
# note: some Benching files are exported with $censored as 'double'
read_contents = function(file) {
  df = read_csv(file.path(path, file))
  #df = df %>%
    #mutate(censored = as.character(censored))
  return(df)
}

# function to check and correct miscounted deaths
# note: use with grouped dataset and within apply()
correct_status = function(row) {
  status = row['status']
  n = row['n']
  censored = row['censored']
  status = as.numeric(status)
  n = as.numeric(n)
  censored = as.numeric(censored)
  if (status > n) {
    return(n - censored)
  } else {
    return(status)
  }
}

# function to extract table from mixed effects model (by David Duneau)
extract_coxme_table = function (mod){
    beta = fixef(mod)
    nvar = length(beta)
    nfrail = nrow(mod$var) - nvar
    se = sqrt(diag(mod$var)[nfrail + 1:nvar])
    z = round(beta/se, 2)
    p = format(as.numeric(pchisq((beta/se)^2, 1,lower.tail = FALSE)), 4)
    table = data.frame(cbind(beta,se,z,p))
    return(table)
}

# function to extract and plot survival data (by David Duneau)
ggplotprep2 <- function(x, times){
  # spreading the survfit data frame into data frame per day 
  d <- data.frame(condition=rep(names(x$strata), x$strata), time=x$time, survival=x$surv, upper=x$upper, lower=x$lower)
  # function to add time point 0 
  fillup0 <- function(s) rbind(c(condition=s, time=0, survival=1, upper=1, lower=1), d[d$condition==s, ], deparse.level = 0)
  # function to determine the missing time points
  indexes <- function(x, time) {
    if(x%in%time) return(x)
    return(time[which.min(abs(time[time<x]-x))])
  }
  # function to complete the missing time points
  fillup <- function(s) {
    d.temp <- d[d$condition==s, ]
    time <- as.numeric(d.temp$time)
    id <- sapply(times, indexes, time=time)
    d.temp <- d.temp[match(id, time), ]
    d.temp$time <- times
    return(d.temp)
  }
  if(times[1]==0) d <- do.call("rbind", sapply(names(x$strata), fillup0, simplify=F))
  d <- do.call("rbind", sapply(names(x$strata), fillup, simplify=F))
  d <- data.frame(Condition=d$condition, Time=as.numeric(d$time), Survival=as.numeric(d$survival), Upper=as.numeric(d$upper), Lower=as.numeric(d$lower))
  return(d)
} 

# additional functions (by David Duneau)
grab_grob <- function(){
  grid.echo()
  grid.grab()
}

RIGHT = function(x,n){
  substring(x,nchar(x)-n+1)
}

LEFT = function(x,n){
  substring(x,1,nchar(x)-n+1)
}

r2.corr.mer <- function(m) {
  lmfit <-  lm(model.response(model.frame(m)) ~ fitted(m))
  summary(lmfit)$r.squared
}

logit2prob <- function(logit){
  odds <- exp(logit)
  prob <- odds / (1 + odds)
  return(prob)
}

`%notin%` = Negate(`%in%`)
```

## Libraries

```{r packages}
library(openxlsx)
library(survival)
library(ggsurvfit)
library(car)
library(gtsummary)
library(survminer)
library(janitor)
library(ggsci)
library(ggtext)
library(mltools)
library(broom)
library(coxme)
library(formatR)
library(tidyverse)
library(cowplot)
library(knitr)
library(stargazer)
```

## Plot Themes

```{r ggplot-survival-theme}
SuperSmallfont= 10
Smallfont= 12
Mediumfont= 14
Largefont= 14
verylargefont = 16
pointsize= 0.7
linesize=0.35
meansize = 1.5
Margin=c(0,0,0,0)

fontsizeaxes = 12
fontsizeaxes2 = 10

basic_theme_surv=
  theme(aspect.ratio = 1,
        panel.background = element_blank(),
        plot.caption =element_text(size=SuperSmallfont,face="italic", hjust = 0.5),
        plot.title = element_text(size=Mediumfont,face="bold", hjust = 0.5),
        plot.subtitle = element_text(size=Smallfont, hjust = 0.5),
        strip.text.x = element_markdown(size =Smallfont, colour = "black",face="italic",hjust = 0.5),
        strip.text.y = element_markdown(size =Smallfont, colour = "black",face="italic",hjust = 0.5),
        strip.background = element_rect(fill=NA, colour="black"),
        strip.placement="outside",
        axis.title.x = element_text(size=Mediumfont,colour="black"),
        axis.title.y = element_text(size=Mediumfont,colour="black"), 
        axis.line.x = element_line(colour="black",size=0.75),
        axis.line.y = element_line(colour="black",size=0.75),
        axis.ticks.x = element_line(size = 0.75),
        axis.ticks.y = element_line(size = 0.75),
        axis.text.x = element_text(size=Smallfont,colour="black"),
        axis.text.y = element_text(size=Smallfont,colour="black"),
        plot.margin = unit(Margin, "cm"),
        legend.direction = "vertical", 
        legend.box = "vertical",
        legend.position = "right",
        legend.key.height = unit(0.4, "cm"),
        legend.key.width= unit(0.6, "cm"),
        legend.title = element_text(face="italic",size=Smallfont), 
        legend.key = element_rect(colour = 'white', fill = "white", linetype='dashed'),
        legend.text = element_text(size=SuperSmallfont),
        legend.background = element_rect(fill=NA))

colours = palette.colors()
```

## Data Import

```{r data-import}
# set path and read data files
path = here::here("data/input")

data_files = list.files(path, 
                        pattern = "*.csv")

# standardise all columns as character variables across all data files
data_list = data.frame(filename = data_files) %>% 
  mutate(file_contents = map(filename, 
                             ~ read_contents(.)))

# unnest the data list into a single data frame
data_raw = unnest(data_list, 
                  cols = file_contents)

# print the result
print(data_raw)
```

## Data Processing 

```{r, data-wrangling-and-formatting}
data_tmp = data_raw %>%
  # Remove unnecessary variables
  select(-filename) %>%
  # Turn character variables into factor ones, except for `$Day_of_infection` and `$Time`
  mutate(across(.cols = where(is.character) & !all_of(c("Day_of_infection", "Time")),
                .fns = as.factor),
         # Create `$Date_Time` as a POSIXct variable
         Date_Time = paste(Day_of_infection, Time, sep = " "),
         Date_Time = as.POSIXct(Date_Time, format = "%d/%m/%Y %H:%M:%S")) %>%
  # Rename `$Vial_ID` as `$Cage_ID`
  rename(Cage_ID = Vial_ID) %>%
  # Arrange rows by the values of `$Date_Time`
  arrange(Date_Time) %>%
  # Group dataset by factor variables
  group_by(across(where(is.factor))) %>%
  # Calculate time difference to create `$Time_to_death`
  mutate(Start_time = first(Date_Time),
         across(c(Start_time, Date_Time), ~as.POSIXct(., format = "%d/%m/%Y %H:%M:%S")),
         Time_to_death = difftime(Date_Time, Start_time, units = "hours"),
         Time_to_death = as.numeric(Time_to_death)) %>%
  # Remove unnecessary variables
  select(-c(Start_time, Date_Time))

# Create dataset with initial sample size for each experimental group
sampled_join = data_tmp %>%
  filter(Time_to_death == 0) %>% 
  group_by(across(where(is.factor))) %>% 
  summarise(Sample_size_sum = Count)

# Create dataset with total number of dead individuals for each experimental group
dead_join = data_tmp %>%
  filter(Censor == 1 & Time_to_death > 0) %>% 
  group_by(across(where(is.factor))) %>% 
  summarise(Dead_sum = sum(Count)) 

# Create dataset to store the number of censored individuals
censored_join = data_tmp %>%
  group_by(across(where(is.factor))) %>% 
  filter(Censor == 0 & Time_to_death > 0) %>% 
  summarise(Censored_sum = sum(Count)) 

# Combine datasets ending in `_join` to calculate the number of survivors and temporarily store values 
survived_tmp = sampled_join %>% 
  left_join(dead_join) %>% 
  left_join(censored_join) %>% 
  mutate(Censored_sum = case_when(is.na(Censored_sum) ~ 0,
                              TRUE ~ Censored_sum),
         Count = Sample_size_sum - (Dead_sum + Censored_sum))

# Create `max_time` dataset to store the last day of scoring for each respective group
max_time = data_tmp %>%
  group_by(across(where(is.factor))) %>% 
  filter(Time_to_death == max(Time_to_death, na.rm = TRUE))

# Create `survived_bind` dataset and join it to `max_time`
# Note: Here, `$Time_to_death` corresponds to the last day of scoring for each respective group
survived_bind = max_time %>%
  left_join(survived_tmp) %>%
  # Remove unnecessary variables
  select(-c(Sample_size_sum, Dead_sum, Censored_sum)) %>% 
  mutate(Censor = 0)

# Create `dead_bind` dataset to store data from dead individuals only
dead_bind = data_tmp %>% 
  filter(Censor == 1 & Time_to_death > 0)

# Create `censored_bind` dataset to store data from censored individuals only
censored_bind = data_tmp %>% 
  filter(Censor == 0 & Time_to_death > 0)

# Combine datasets ending in `_bind` and create final `data` dataset
data = bind_rows(censored_bind, dead_bind, survived_bind) %>% 
  # Format `$Time_to_death` 
  mutate(Time_to_death = case_when(Time_to_death > 0 & Time_to_death <= 8 ~ 8,
                                   #Time_to_death > 2 & Time_to_death <= 4 ~ 4,
                                   #Time_to_death > 4 & Time_to_death <= 8 ~ 8,
                                   Time_to_death > 8 & Time_to_death <= 16 ~ 16,
                                   Time_to_death > 16 & Time_to_death <= 24 ~ 24,
                                   Time_to_death > 24 & Time_to_death <= 32 ~ 32,
                                   Time_to_death > 32 & Time_to_death <= 40 ~ 40,
                                   Time_to_death > 40 & Time_to_death <= 48 ~ 48,
                                   Time_to_death > 48 & Time_to_death <= 56 ~ 56,
                                   Time_to_death > 56 & Time_to_death <= 64 ~ 64,
                                   Time_to_death > 64 & Time_to_death <= 72 ~ 72,
                                   TRUE ~ Time_to_death),
         # Reorder factor levels in `$Age` and `$Treatment`
         Age = fct_relevel(Age, c("7 days", "35 days")),
         Treatment = fct_relevel(Treatment, c("Untreated", "Rapamycin"))) %>% 
  # Generated row IDs
  rowid_to_column()
```

```{r data-check-and-export}
# Create dataset with the total number of scored individuals per experimental group
scored = data %>%
  filter(Time_to_death < max(Time_to_death)) %>% 
  group_by(across(where(is.factor))) %>% 
  summarise(Scored_sum = sum(Count))

# Check for miscounted data by calculating the difference between starting sample size 
# and the total number of scored individuals
negative_values = left_join(sampled_join, scored) %>% 
  mutate(Final_count = Sample_size_sum - Scored_sum) %>% 
  filter(Final_count < 0)

# Print experimental groups showing negative values in `$Final_count`
print(negative_values)

# Export dataset as CSV file
# Note: Dataset is not yet expanded
write_csv(data, "data/output/exp_010_systemic.csv")
```

# Survival {.tabset}

```{r data-expansion, fig.dim=c(4, 4), fig.align='center', out.width="75%"}
data_expanded = data %>%
  # Remove original row IDs
  select(-rowid) %>%
  # Expand dataset by duplicating rows according to values from `$Count`
  uncount(Count) %>%
  # Generate new row IDs
  rowid_to_column() %>% 
  # Turn `$Day_of_infection` into factor
  mutate(Day_of_infection = as.factor(Day_of_infection))
```

```{r plot-caption}
# Summarise the sample size
num_observations = sampled_join %>% 
  group_by(Line) %>% 
  summarise(Count = sum(Sample_size_sum), .groups = "drop")

# Store sample size values as text for later use as plot caption
plot_caption = num_observations %>% 
  mutate(summary = paste(Line, "=", Count)) %>% 
  pull(summary) %>% 
  paste(collapse = "; ")
```

## Across Lines

```{r survival-by-line, fig.dim=c(6, 6), fig.align='center', out.width="75%"}
fit_genotype = survfit(Surv(Time_to_death, Censor) ~ Treatment + Age + Line,
                   data = data_expanded)

plot_genotype = ggplotprep2(fit_genotype, times = c(seq(0, 56, by = 8))) %>%
  mutate(Condition = str_remove_all(Condition,"[a-zA-Z]*=")) %>%
  separate(Condition, c("Treatment", "Age", "Line"), sep = ", ") %>% 
  mutate(across(where(is.character), as.factor),
         Treatment = fct_relevel(Treatment, rev),
         Age = fct_relevel(Age, rev))

ggplot(plot_genotype, aes(x = Time, y = Survival, colour = Treatment)) +
  facet_grid(~Line) +
  geom_hline(yintercept = 0.5, linetype = "dotted") +
  geom_vline(xintercept = 48, colour = "red", linetype = "dotted") +
  geom_line(aes(linetype = Age), linewidth = 1) +
  geom_point(colour = "black", size = 1) +
  scale_color_manual(values = colours[c(1,7)]) +
  scale_linetype_manual(values = c("solid", "dashed")) +
  labs(title = "Survival to systemic P. rettgeri infection",
       caption = paste("Number of observations (n) per genotype:", plot_caption)) +
  scale_y_continuous("Proportion of survivors",
                     limits = c(0, 1),
                     breaks = c(0, 0.2, 0.4, 0.6, 0.8, 1)) +
  scale_x_continuous("Time (hours post-infection)",
                     breaks = c(seq(0, 56, by = 8))) +
  basic_theme_surv 
```

## Across Lines and Replicates

```{r survival-by-line-and-replicate, fig.dim=c(7, 7), fig.align='center', out.width="75%"}
fit_replicate = survfit(Surv(Time_to_death, Censor) ~ Treatment + Age + Line + Internal_replicate,
                   data = data_expanded)

plot_replicate = ggplotprep2(fit_replicate, times = c(seq(0, 56, by = 8))) %>%
  mutate(Condition = str_remove_all(Condition,"[a-zA-Z]*=")) %>%
  separate(Condition, c("Treatment", "Age", "Line", "Internal_replicate"), sep = ", ") %>% 
  mutate(across(where(is.character), as.factor),
         Treatment = fct_relevel(Treatment, rev),
         Age = fct_relevel(Age, rev))

ggplot(plot_replicate, aes(x = Time, y = Survival, colour = Treatment)) +
  facet_grid(~Internal_replicate~Line) +
  geom_hline(yintercept = 0.5, linetype = "dotted") +
  geom_vline(xintercept = 48, colour = "red", linetype = "dotted") +
  geom_line(aes(linetype = Age), linewidth = 1) +
  geom_point(colour = "black", size = 1) +
  scale_color_manual(values = colours[c(1,7)]) +
  scale_linetype_manual(values = c("solid", "dashed")) +
  labs(title = "Survival to systemic P. rettgeri infection",
       caption = paste("Number of observations (n) per genotype:", plot_caption)) +
  scale_y_continuous("Proportion of survivors",
                     limits = c(0, 1),
                     breaks = c(0, 0.2, 0.4, 0.6, 0.8, 1)) +
  scale_x_continuous("Time (hours post-infection)",
                     breaks = c(seq(0, 56, by = 8))) +
  basic_theme_surv +
  theme(strip.text.y = element_markdown(size = SuperSmallfont, 
                                        colour = "black",
                                        face = "italic", 
                                        hjust = 0.5))
```

## Across Lines and Sexes

```{r survival-by-line-and-sex, fig.dim=c(6, 6), fig.align='center', out.width="75%"}
fit_sex = survfit(Surv(Time_to_death, Censor) ~ Treatment + Age + Line + Sex,
                   data = data_expanded)

plot_sex = ggplotprep2(fit_sex, times = c(seq(0, 56, by = 8))) %>%
  mutate(Condition = str_remove_all(Condition,"[a-zA-Z]*=")) %>%
  separate(Condition, c("Treatment", "Age", "Line", "Sex"), sep = ", ") %>% 
  mutate(across(where(is.character), as.factor),
         Treatment = fct_relevel(Treatment, rev),
         Age = fct_relevel(Age, rev))

ggplot(plot_sex, aes(x = Time, y = Survival, colour = Treatment)) +
  facet_grid(~Sex~Line) +
  geom_hline(yintercept = 0.5, linetype = "dotted") +
  geom_vline(xintercept = 48, colour = "red", linetype = "dotted") +
  geom_line(aes(linetype = Age), linewidth = 1) +
  geom_point(colour = "black", size = 1) +
  scale_color_manual(values = colours[c(1,7)]) +
  scale_linetype_manual(values = c("solid", "dashed")) +
  labs(title = "Survival to systemic P. rettgeri infection",
       caption = paste("Number of observations (n) per genotype:", plot_caption)) +
  scale_y_continuous("Proportion of survivors",
                     limits = c(0, 1),
                     breaks = c(0, 0.2, 0.4, 0.6, 0.8, 1)) +
  scale_x_continuous("Time (hours post-infection)",
                     breaks = c(seq(0, 56, by = 8))) +
  basic_theme_surv
```

# Regression {.tabset}

<br><br>

## *wDah* 

<br><br>

### Model 1

```{r wdah-model-1, results='hold'}
data_wdah = data_expanded %>% 
  filter(Line =="wDah")

model1 = coxme(Surv(Time_to_death, Censor) ~ 
                         Age + Treatment + Sex + (1|Internal_replicate) + (1|Cage_ID), 
                       data = data_wdah)
summary(model1) 
```
<br><br>

### Model 2

```{r wdah-model-2, results='hold'}
model2 = coxme(Surv(Time_to_death, Censor) ~ 
                         Age + Treatment + Sex + Treatment*Sex + (1|Internal_replicate) + (1|Cage_ID), 
                       data = data_wdah)
summary(model2)
```
<br><br>

### Likelihood Ratio Test

```{r wdah-lrt, results='hold'}
test1 = anova(model1, model2)
print(test1)
```
<br><br>

### Best Model

```{r wdah-best-model, results='hold'}
best_model = model1
model_formula = str_replace_all(deparse(formula(best_model), 
                                        width.cutoff = 500), 
                                c("_" = "\\\\_"))  
```

<div align="center">
$`r model_formula`$

<div class = "row">
<div class = "col-md-6">
```{r wdah-coxme-table, results='hold'}
coxme_table = extract_coxme_table(best_model)
coxme_table$beta_lower = confint(best_model)[,1]
coxme_table$beta_upper = confint(best_model)[,2]

coxme_table = rownames_to_column(coxme_table, "Parameter")
coxme_table = coxme_table %>%
  mutate(across(beta:beta_upper, as.numeric)) %>% 
  add_row(Parameter = "Baseline",
          beta = 0,
          se = 0,
          z = 0,
          p = 0,
          beta_lower = 0,
          beta_upper = 0) %>%
  mutate(Parameter = as_factor(Parameter) %>%
           fct_relevel("Baseline"))

tbl_regression(best_model,
                          exponentiate = FALSE) %>%
  modify_header(update = c(estimate ~ "**log(HR)**",
                           label ~ "**Parameter**")) %>%
  italicize_levels() %>% 
  as_flex_table() %>% 
  flextable::set_table_properties(width = .5)
```
</div>

<div class = "col-sm-6">
```{r wdah-coxme-plot, results='hold', fig.dim=c(3,5), out.width="80%"}
model_plot = ggplot(coxme_table,
        aes(x = Parameter,
            y = beta)) +
   geom_errorbar(aes(ymin = beta_lower,
                     ymax = beta_upper),
                 col = "black",
                 width = 0.17,
                 size = 0.5,
                 show.legend = FALSE) +
   geom_point(stat = "identity",
              show.legend = FALSE,
              size = 1.5,
              #position = position_dodge(0.2)
              ) +
   geom_hline(yintercept = 0,
              colour = "red",
              linetype = 4) +
   scale_color_manual(values = c("red","blue","green","orange","black")) +
   scale_x_discrete(expand = c(0.1, 0)) +
   scale_y_continuous("log(HR) (95 % CI)",   
                        breaks = c(seq(-5, 5, by = 1))) +
   coord_cartesian(ylim = c(-2, 2), 
                   expand = TRUE, 
                   clip = "on") +
   xlab("") +                                                                    
   theme_cowplot() +
   theme(axis.title.y = ggtext::element_markdown(),
         axis.text.x = element_text(angle = 45,
                                    hjust = 1,
                                    size = 14),
         aspect.ratio = 2)    

print(model_plot)
```
</div>
</div>

## *DGRP OX* 

<br><br>

### Model 1

```{r ox-model-1, results='hold'}
data_ox = data_expanded %>% 
  filter(Line =="DGRP OX")

model1 = coxme(Surv(Time_to_death, Censor) ~ 
                         Age + Treatment + Sex + (1|Internal_replicate) + (1|Cage_ID), 
                       data = data_ox)
summary(model1) 
```
<br><br>

### Model 2

```{r ox-model-2, results='hold'}
model2 = coxme(Surv(Time_to_death, Censor) ~ 
                         Age + Treatment + Sex + Treatment*Sex + (1|Internal_replicate) + (1|Cage_ID), 
                       data = data_ox)
summary(model2)
```
<br><br>

### Likelihood Ratio Test

```{r ox-lrt, results='hold'}
test1 = anova(model1, model2)
print(test1)
```
<br><br>

### Best Model

```{r ox-best-model, results='hold'}
best_model = model1
model_formula = str_replace_all(deparse(formula(best_model), 
                                        width.cutoff = 500), 
                                c("_" = "\\\\_"))  
```
<br><br>

<div align="center">
$`r model_formula`$

<div class = "row">
<div class = "col-md-6">
```{r ox-coxme-table, results='hold'}
coxme_table = extract_coxme_table(best_model)
coxme_table$beta_lower = confint(best_model)[,1]
coxme_table$beta_upper = confint(best_model)[,2]

coxme_table = rownames_to_column(coxme_table, "Parameter")
coxme_table = coxme_table %>%
  mutate(across(beta:beta_upper, as.numeric)) %>% 
  add_row(Parameter = "Baseline",
          beta = 0,
          se = 0,
          z = 0,
          p = 0,
          beta_lower = 0,
          beta_upper = 0) %>%
  mutate(Parameter = as_factor(Parameter) %>%
           fct_relevel("Baseline"))

tbl_regression(best_model,
                          exponentiate = FALSE) %>%
  modify_header(update = c(estimate ~ "**log(HR)**",
                           label ~ "**Parameter**")) %>%
  italicize_levels() %>% 
  as_flex_table() %>% 
  flextable::set_table_properties(width = .5)
```
</div>

<div class = "col-sm-6">
```{r ox-coxme-plot, results='hold', fig.dim=c(3,5), out.width="80%"}
model_plot = ggplot(coxme_table,
        aes(x = Parameter,
            y = beta)) +
   geom_errorbar(aes(ymin = beta_lower,
                     ymax = beta_upper),
                 col = "black",
                 width = 0.17,
                 size = 0.5,
                 show.legend = FALSE) +
   geom_point(stat = "identity",
              show.legend = FALSE,
              size = 1.5,
              #position = position_dodge(0.2)
              ) +
   geom_hline(yintercept = 0,
              colour = "red",
              linetype = 4) +
   scale_color_manual(values = c("red","blue","green","orange","black")) +
   scale_x_discrete(expand = c(0.1, 0)) +
   scale_y_continuous("log(HR) (95 % CI)",   
                        breaks = c(seq(-5, 5, by = 1))) +
   coord_cartesian(ylim = c(-2, 2), 
                   expand = TRUE, 
                   clip = "on") +
   xlab("") +                                                                    
   theme_cowplot() +
   theme(axis.title.y = ggtext::element_markdown(),
         axis.text.x = element_text(angle = 45,
                                    hjust = 1,
                                    size = 14),
         aspect.ratio = 2)    

print(model_plot)
```
</div>
</div>

```{r session-info, echo = FALSE}
sessionInfo()
```
