---
title: "Experiment 010"
subtitle: "Effect of Rapamycin Treatment on Survival to Systemic Infection with *P. rettgeri* "
author: "by Barbara Black"
date: "Last compiled on `r format(Sys.time(), '%d %B, %Y')`"
output: 
    html_document:
      code_folding: hide
      number_sections: true
      toc: true
      toc_float: true
      toc_depth: 3
      fig_caption: true
      theme: united
      css: style.css
      highlight: zenburn
editor_options: 
  chunk_output_type: console
---

<style>

/* Change font size of the title */
h1.title {
  font-size: 22px;
}

/* Define the frames */
div.blue { background-color:#e6f0ff; border-radius: 1px; padding: 10px; }
div.orange { background-color:#fff8dc; border-radius: 5px; padding: 20px; margin: 10px 0;}
div.green { background-color:#00bbc6; border-radius: 5px; padding: 20px;
  border: 1px solid #000; margin: 10px 0;}

/* Headers */ 
h1 { font-size: 18px; font-weight: bold;}
h2 { font-size: 16px; font-weight: bold; margin: 10px 0;}
h3 { font-size: 14px; font-weight: bold; margin: 10px 0;}

/* Change font size of the table of contents */
TOC { font-size: 12px; }
</style>

```{r chunk-setup}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, results = 'hide', dpi = 300)
```

# Background

# Code {.tabset}

## Functions

```{r survival-functions}
# function to change code chunk size in output
# note: automatically applied when chunk runs
def.chunk.hook = knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x = def.chunk.hook(x, options)
  ifelse(options$size != "normalsize", paste0("\n \\", options$size,"\n\n", x, "\n\n \\normalsize"), x)
})

# function to turn $censored into 'character' across all files
# note: some Benching files are exported with $censored as 'double'
read_contents = function(file) {
  df = read_csv(file.path(path, file))
  #df = df %>%
    #mutate(censored = as.character(censored))
  return(df)
}

# function to check and correct miscounted deaths
# note: use with grouped dataset and within apply()
correct_status = function(row) {
  status = row['status']
  n = row['n']
  censored = row['censored']
  status = as.numeric(status)
  n = as.numeric(n)
  censored = as.numeric(censored)
  if (status > n) {
    return(n - censored)
  } else {
    return(status)
  }
}

# function to extract table from mixed effects model (by David Duneau)
extract_coxme_table = function (mod){
    beta = fixef(mod)
    nvar = length(beta)
    nfrail = nrow(mod$var) - nvar
    se = sqrt(diag(mod$var)[nfrail + 1:nvar])
    z = round(beta/se, 2)
    p = format(as.numeric(pchisq((beta/se)^2, 1,lower.tail = FALSE)), 4)
    table = data.frame(cbind(beta,se,z,p))
    return(table)
}

# function to extract and plot survival data (by David Duneau)
ggplotprep2 <- function(x, times){
  # spreading the survfit data frame into data frame per day 
  d <- data.frame(condition=rep(names(x$strata), x$strata), time=x$time, survival=x$surv, upper=x$upper, lower=x$lower)
  # function to add time point 0 
  fillup0 <- function(s) rbind(c(condition=s, time=0, survival=1, upper=1, lower=1), d[d$condition==s, ], deparse.level = 0)
  # function to determine the missing time points
  indexes <- function(x, time) {
    if(x%in%time) return(x)
    return(time[which.min(abs(time[time<x]-x))])
  }
  # function to complete the missing time points
  fillup <- function(s) {
    d.temp <- d[d$condition==s, ]
    time <- as.numeric(d.temp$time)
    id <- sapply(times, indexes, time=time)
    d.temp <- d.temp[match(id, time), ]
    d.temp$time <- times
    return(d.temp)
  }
  if(times[1]==0) d <- do.call("rbind", sapply(names(x$strata), fillup0, simplify=F))
  d <- do.call("rbind", sapply(names(x$strata), fillup, simplify=F))
  d <- data.frame(Condition=d$condition, Time=as.numeric(d$time), Survival=as.numeric(d$survival), Upper=as.numeric(d$upper), Lower=as.numeric(d$lower))
  return(d)
} 

# additional functions (by David Duneau)
grab_grob <- function(){
  grid.echo()
  grid.grab()
}

RIGHT = function(x,n){
  substring(x,nchar(x)-n+1)
}

LEFT = function(x,n){
  substring(x,1,nchar(x)-n+1)
}

r2.corr.mer <- function(m) {
  lmfit <-  lm(model.response(model.frame(m)) ~ fitted(m))
  summary(lmfit)$r.squared
}

logit2prob <- function(logit){
  odds <- exp(logit)
  prob <- odds / (1 + odds)
  return(prob)
}

`%notin%` = Negate(`%in%`)
```

## Libraries

```{r packages}
library(openxlsx)
library(survival)
library(ggsurvfit)
library(car)
library(gtsummary)
library(survminer)
library(janitor)
library(ggsci)
library(ggtext)
library(mltools)
library(broom)
library(coxme)
library(formatR)
library(tidyverse)
library(cowplot)
library(knitr)
```

## Themes | `ggplot()`

```{r ggplot-survival-theme}
SuperSmallfont= 10
Smallfont= 12
Mediumfont= 14
Largefont= 14
verylargefont = 16
pointsize= 0.7
linesize=0.35
meansize = 1.5
Margin=c(0,0,0,0)

fontsizeaxes = 12
fontsizeaxes2 = 10

basic_theme_surv=
  theme(aspect.ratio = 1,
        panel.background = element_blank(),
        plot.caption =element_text(size=SuperSmallfont,face="italic", hjust = 1.5),
        plot.title = element_text(size=Mediumfont,face="bold", hjust = 0.5),
        plot.subtitle = element_text(size=Smallfont, hjust = 0.5),
        strip.text.x = element_markdown(size =Smallfont, colour = "black",face="italic",hjust = 0.5),
        strip.text.y = element_markdown(size =Smallfont, colour = "black",face="italic",hjust = 0.5),
        strip.background = element_rect(fill=NA, colour="black"),
        strip.placement="outside",
        axis.title.x = element_text(size=Mediumfont,colour="black"),
        axis.title.y = element_text(size=Mediumfont,colour="black"), 
        axis.line.x = element_line(colour="black",size=0.75),
        axis.line.y = element_line(colour="black",size=0.75),
        axis.ticks.x = element_line(size = 0.75),
        axis.ticks.y = element_line(size = 0.75),
        axis.text.x = element_text(size=Smallfont,colour="black"),
        axis.text.y = element_text(size=Smallfont,colour="black"),
        plot.margin = unit(Margin, "cm"),
        legend.direction = "vertical", 
        legend.box = "vertical",
        legend.position = "right",
        legend.key.height = unit(0.4, "cm"),
        legend.key.width= unit(0.6, "cm"),
        legend.title = element_text(face="italic",size=Smallfont), 
        legend.key = element_rect(colour = 'white', fill = "white", linetype='dashed'),
        legend.text = element_text(size=SuperSmallfont),
        legend.background = element_rect(fill=NA))

colours = palette.colors()
```

## Data Import

```{r data-import}
# set path and read data files
path = here::here("data/input")

data_files = list.files(path, 
                        pattern = "*.csv")

# standardise all columns as character variables across all data files
data_list = data.frame(filename = data_files) %>% 
  mutate(file_contents = map(filename, 
                             ~ read_contents(.)))

# unnest the data list into a single data frame
data_raw = unnest(data_list, 
                  cols = file_contents)

# print the result
print(data_raw)
```

## Data Processing 

```{r data-wrangling-and-formatting}
data = data_raw %>%
  # Remove unnecessary variables
  select(-filename) %>%
  # Turn character variables into factor ones, except for `$Day_of_infection` and `$Time`
  mutate(across(.cols = where(is.character) & !all_of(c("Day_of_infection", "Time")), 
                .fns = as.factor),
         Date_Time = paste(Day_of_infection, Time, sep = " "),
         Date_Time = as.POSIXct(Date_Time, format = "%d/%m/%Y %H:%M:%S")) %>%
  # Arrange rows by the values of `$date_time`
  arrange(Date_Time) %>%
  # Group dataset by factor variables
  group_by(across(where(is.factor))) %>%
  # Calculate time difference to create `$Time_to_death`
  mutate(Start_time = first(Date_Time),
         across(c(Start_time, Date_Time), ~as.POSIXct(., format = "%d/%m/%Y %H:%M:%S")),
         Time_to_death = difftime(Date_Time, Start_time, units = "hours"),
         Time_to_death = as.numeric(Time_to_death),
         Time_to_death = case_when(Time_to_death > 0 & Time_to_death <= 8 ~ 8,
                                   #Time_to_death > 2 & Time_to_death <= 4 ~ 4,
                                   #Time_to_death > 4 & Time_to_death <= 8 ~ 8,
                                   Time_to_death > 8 & Time_to_death <= 16 ~ 16,
                                   Time_to_death > 16 & Time_to_death <= 24 ~ 24,
                                   Time_to_death > 24 & Time_to_death <= 32 ~ 32,
                                   Time_to_death > 32 & Time_to_death <= 40 ~ 40,
                                   Time_to_death > 40 & Time_to_death <= 48 ~ 48,
                                   Time_to_death > 48 & Time_to_death <= 56 ~ 56,
                                   TRUE ~ Time_to_death)) %>%
  # Remove unnecessary variables
  select(-c(Start_time, Date_Time)) %>% 
  # Generate row IDs
  rowid_to_column()
```

```{r data-check-and-export}
# Create dataset with initial sample size for each experimental group
sample_size = data %>%
  filter(Time_to_death == 0) %>% 
  group_by(across(where(is.factor))) %>% 
  summarise(Sample_size = Count)

# Create dataset with total number of scored flies for each experimental group
scored = data %>%
  filter(Time_to_death > 0) %>% 
  group_by(across(where(is.factor))) %>% 
  summarise(Events = sum(Count))

# Check for miscounted data by calculating the difference between sample size and total number of scored flies, and then searching for negative `$Final_count` values
negative_values = left_join(sample_size, scored) %>% 
  mutate(Final_count = Sample_size - Events) %>% 
  filter(Final_count < 0)

# Print experimental groups showing negative count values
print(negative_values)

# Export dataset as CSV file
# Note: Dataset is not yet expanded
write_csv(data, "data/output/exp_010_systemic.csv")
```

# Survival

```{r data-expansion-and-survival, fig.dim=c(4, 4), fig.align='center', out.width="75%"}
data_expanded = data %>%
  # Remove original row IDs
  select(-rowid) %>%
  # Expand dataset by duplicating rows according to values from `$Count`
  uncount(Count) %>%
  # Generate new row IDs
  rowid_to_column() 

fit = survfit(Surv(Time_to_death, Censor) ~ Treatment + Age,
                   data = data_expanded)

plot = ggplotprep2(fit, times = c(seq(0, 48, by = 8))) %>%
  mutate(Condition = str_remove_all(Condition,"[a-zA-Z]*=")) %>%
  separate(Condition, c("Treatment", "Age"), sep = ", ") %>% 
  mutate(across(where(is.character), as.factor),
         Treatment = fct_relevel(Treatment, rev),
         Age = fct_relevel(Age, rev))

ggplot(plot, aes(x = Time, y = Survival, colour = Treatment)) +
  #facet_grid(~) +
  geom_hline(yintercept = 0.5, linetype = "dotted") +
  geom_line(aes(linetype = Age), linewidth = 1) +
  geom_point(colour = "black", size = 1) +
  scale_color_manual(values = colours[c(1,7)]) +
  scale_linetype_manual(values = c("solid", "dashed")) +
  labs(title = "Effect of rapamycin treatment \non survival to systemic \nP. rettgeri infection",
       caption = "Note: Pooled sexes and genotypes") +
  scale_y_continuous("Proportion of survivors",
                     limits = c(0, 1),
                     breaks = c(0, 0.2, 0.4, 0.6, 0.8, 1)) +
  scale_x_continuous("Time (days post-infection)",
                     breaks = c(seq(0, 48, by = 8))) +
  basic_theme_surv
```

```{r survival-by-sex, fig.dim=c(5, 5), fig.align='center', out.width="75%"}
fit_sex = survfit(Surv(Time_to_death, Censor) ~ Treatment + Age + Sex,
                   data = data_expanded)

plot_sex = ggplotprep2(fit_sex, times = c(seq(0, 48, by = 8))) %>%
  mutate(Condition = str_remove_all(Condition,"[a-zA-Z]*=")) %>%
  separate(Condition, c("Treatment", "Age", "Sex"), sep = ", ") %>% 
  mutate(across(where(is.character), as.factor),
         Treatment = fct_relevel(Treatment, rev),
         Age = fct_relevel(Age, rev))

ggplot(plot_sex, aes(x = Time, y = Survival, colour = Treatment)) +
  facet_grid(~Sex) +
  geom_hline(yintercept = 0.5, linetype = "dotted") +
  geom_line(aes(linetype = Age), linewidth = 1) +
  geom_point(colour = "black", size = 1) +
  scale_color_manual(values = colours[c(1,7)]) +
  scale_linetype_manual(values = c("solid", "dashed")) +
  labs(title = "Effect of rapamycin treatment on survival \nto systemic P. rettgeri infection \nin males and females",
       caption = "Note: Pooled genotypes") +
  scale_y_continuous("Proportion of survivors",
                     limits = c(0, 1),
                     breaks = c(0, 0.2, 0.4, 0.6, 0.8, 1)) +
  scale_x_continuous("Time (days post-infection)",
                     breaks = c(seq(0, 48, by = 8))) +
  basic_theme_surv
```

```{r survival-by-sex-and-genotype, fig.dim=c(5, 5), fig.align='center', out.width="75%"}
fit_genotype = survfit(Surv(Time_to_death, Censor) ~ Treatment + Age + Sex + Line,
                   data = data_expanded)

plot_genotype = ggplotprep2(fit_genotype, times = c(seq(0, 48, by = 8))) %>%
  mutate(Condition = str_remove_all(Condition,"[a-zA-Z]*=")) %>%
  separate(Condition, c("Treatment", "Age", "Sex", "Line"), sep = ", ") %>% 
  mutate(across(where(is.character), as.factor),
         Treatment = fct_relevel(Treatment, rev),
         Age = fct_relevel(Age, rev))

ggplot(plot_genotype, aes(x = Time, y = Survival, colour = Treatment)) +
  facet_grid(~Line~Sex) +
  geom_hline(yintercept = 0.5, linetype = "dotted") +
  geom_line(aes(linetype = Age), linewidth = 1) +
  geom_point(colour = "black", size = 1) +
  scale_color_manual(values = colours[c(1,7)]) +
  scale_linetype_manual(values = c("solid", "dashed")) +
  labs(title = "Effect of rapamycin treatment on survival \nto systemic P. rettgeri infection \nin males and females across genotypes") +
       #caption = "") +
  scale_y_continuous("Proportion of survivors",
                     limits = c(0, 1),
                     breaks = c(0, 0.2, 0.4, 0.6, 0.8, 1)) +
  scale_x_continuous("Time (days post-infection)",
                     breaks = c(seq(0, 48, by = 8))) +
  basic_theme_surv
```

```{r session-info, echo = FALSE}
sessionInfo()
```